Sustainable computational science:\\ the ReScience initiative

### 2017-11-09 draft.tex
Missing references and finishing touches

Containerization, as implemented e.g. by Docker \citep{docker} is
currently much discussed, but provides only the executable version
without a human-readable description. Moreover, the long-term
stability of the container file format remains to be
evaluated. History has shown that long-term stability in computing
technology is achieved only by conventions for which it is a design
priority, for example the Java Virtual Machine \citep{JVM}. Docker, on
the contrary, is developed as a deployment technology with no ambition
towards long-term archiving.

>>>>

Containerization, as implemented e.g. by Docker \citep{docker} is
currently much discussed, but provides only the executable version
without a human-readable description. Moreover, the long-term
stability of the container file format remains to be
evaluated. History has shown that long-term stability in computing
technology is achieved only by technology for which it is a design
priority, as in the case of the Java Virtual Machine
\citep{JVM}. Docker, on the contrary, is promoted as a deployment
technology with no visible ambition towards archiving of computational
environments.
